Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-06-06 preproc/Analysis_exp7_prepro.rmd
add preprocessing code

---
title: "Quality_Control_&_Preprocessing_for_Moral_Categ_Replication"
author: "hcp"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---
<style type="text/css">

@@

```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# get the file names for files contain "data_exp7_rep_match_"
fNames.m <- list.files(path = "./data/", pattern = "data_exp7_rep_match_*")
# add the directory information to the filenames
fNames.m <- paste('./data/',fNames.m, sep = '')

@@

# do the same to data from categorization, get the raw data for categorization task
fNames.c <- list.files(path = "./data/", pattern = "data_exp7_rep_categ_*")
fNames.c <- paste('./data/',fNames.c, sep = '')
df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))

@@

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
df.L1 <- df.L[,c("Subject", "Age", "Sex", "Match", "Morality", "Identity", "ACC","RT")]
df.T1 <- df.T[,c("Subject", "Age", "Sex", "Task", "Morality", "Identity", "ACC","RT")]
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

# write files
setwd('..')
write.csv(df.L1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
write.csv(df.L1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
write.csv(df.L1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
setwd('./preproc')

@@

# write files to an upper-lelel folder
setwd('..')
write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
setwd('./preproc')
```

```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}

df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
df.L1.V.sum_rt_acc_l_p$cond <- paste(df.L1.V.sum_rt_acc_l_p$Morality,df.L1.V.sum_rt_acc_l_p$Identity,sep = '_')
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l_p,Morality == 'Good')
ggplot(data=df.L1.V.sum_rt_acc_l_p, aes(x=cond, y=RT, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

@@

>>>>

---
title: "Preprocessing_&_Plot_for_Moral_Categ_Replication"
author: "hcp"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---
<style type="text/css">

@@

```{r loadingData_e7,,echo=FALSE,results='hide',warning=FALSE, message=FALSE}
# set the directories
curDir <- getwd()   # directory for preprocessing
rootDir <- gsub('.{7}$', '', curDir)
rawDir <- paste(curDir,'/data/',sep = '')
traDir <- paste(rootDir,'tradAnal',sep = '')
ddmDir <- paste(rootDir,'hddmMod',sep = '')

# get the file names for files contain "data_exp7_rep_match_"
fNames.m <- list.files(path = rawDir, pattern = "data_exp7_rep_match_*")
# add the directory information to the filenames
fNames.m <- paste(rawDir,fNames.m, sep = '')

@@

# do the same to data from categorization, get the raw data for categorization task
fNames.c <- list.files(path = rawDir, pattern = "data_exp7_rep_categ_*")
fNames.c <- paste(rawDir,fNames.c, sep = '')
df.T    <- do.call("rbind",lapply(as.list(fNames.c),FUN=function(files){read.table(files, header=TRUE, sep="",stringsAsFactors=F)}))

@@

```{r clean the data_e7,echo=FALSE,results='hide',warning=FALSE, message=FALSE}

# get the data file for hddm analysis
df.L.hddm <- subset(df.L, ACC ==1 | ACC == 0)  # remove non-response trials or pressing wrong key
df.T.hddm <- subset(df.T, ACC ==1 | ACC == 0)

df.L.hddm_m <- subset(df.L.hddm, Match == 'match') # select data
df.L.hddm_m <- df.L.hddm_m[,c('Subject','Morality','Identity','RT','ACC')] # select column
colnames(df.L.hddm_m) <- c("subj_idx","Morality",'id','rt','response')     # change column name

df.L.hddm_nm <- subset(df.L.hddm, Match == 'mismatch')
df.L.hddm_nm <- df.L.hddm_nm[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.L.hddm_nm) <- c("subj_idx","Morality",'id','rt','response')

df.T.hddm_val <- subset(df.T.hddm, Task == 'Val')
df.T.hddm_val <- df.T.hddm_val[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_val) <- c("subj_idx","Morality",'id','rt','response')
df.T.hddm_id <- subset(df.T.hddm, Task == 'Id')
df.T.hddm_id <- df.T.hddm_id[,c('Subject','Morality','Identity','RT','ACC')]
colnames(df.T.hddm_id) <- c("subj_idx","Morality",'id','rt','response')

setwd(ddmDir)
write.csv(df.L.hddm_m,'exp7_rep_match_hddm.csv',row.names = F)
write.csv(df.L.hddm_nm,'exp7_rep_mismatch_hddm.csv',row.names = F)
write.csv(df.T.hddm_val,'exp7_rep_categ_val_hddm.csv',row.names = F)
write.csv(df.T.hddm_id,'exp7_rep_categ_id_hddm.csv',row.names = F)
rm('df.L.hddm','df.T.hddm','df.L.hddm_m','df.L.hddm_nm','df.T.hddm_val','df.T.hddm_id')
setwd(curDir)

# clean data for trad. analysis
df.L1 <- df.L[,c("Subject", "Age", "Sex", "Match", "Morality", "Identity", "ACC","RT")]
df.T1 <- df.T[,c("Subject", "Age", "Sex", "Task", "Morality", "Identity", "ACC","RT")]
df.L1$RT <- df.L1$RT * 1000 # transfer from seconds to min seconds
df.T1$RT <- df.T1$RT * 1000 # careful about the scale of time when using HDDM or ex-Gaussian

@@

# write files
setwd(traDir)
write.csv(df.L1.V.sum_w,'exp7_rep_match_behav_wide.csv',row.names = F)
write.csv(df.L1.V.SDT_l,'exp7_rep_match__dprime_long.csv',row.names = F)
write.csv(df.L1.V.sum_rt_acc_l,'exp7_rep_match__rt_acc_long.csv',row.names = F)
setwd(curDir)

@@

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.T1.V.sum_w,'exp7_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.T1.V.sum_rt_acc_l,'exp7_rep_categ__rt_acc_long.csv',row.names = F)
setwd(curDir)

```{r plot_ind_data,echo=FALSE,warning=FALSE, message=FALSE}
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l,Match == 'match')
df.L1.V.sum_rt_acc_l_p$cond <- paste(df.L1.V.sum_rt_acc_l_p$Morality,df.L1.V.sum_rt_acc_l_p$Identity,sep = '_')
df.L1.V.sum_rt_acc_l_p <- subset(df.L1.V.sum_rt_acc_l_p,Morality == 'Good')
ggplot(data=df.L1.V.sum_rt_acc_l_p, aes(x=cond, y=RT, group=Subject, colour=Subject)) +
    geom_line() +
    geom_point() +
    apatheme

@@

#ggstatsplot::ggbetweenstats(
#  data = df.L1.V.sum_rt_acc_l_p,
#  x = c(Morality,Identity),
#  y = RT,
#  notch = TRUE,                                   # show notched box plot
#  mean.plotting = TRUE,                           # whether mean for each group id to be displayed 
#  #type = "parametric",                            # which type of test is to be run
#  outlier.tagging = FALSE,                         # whether outliers need to be tagged
#  #outlier.label = RT,                    # variable to be used for the outlier tag
#  xlab = "conditions",                       # label for the x-axis variable
#  ylab = "Reaction time (ms)",               # label for the y-axis variable
#  title = "Dataset: Iris flower data set",        # title text for the plot
#  caption = expression(                           # caption text for the plot 
#    paste(italic("Note"), ": this is a demo")
#  ),
#  messages = FALSE
#) +                                               # further modification outside of ggstatsplot
#  ggplot2::coord_cartesian(ylim = c(500, 800)) + 
#  ggplot2::scale_y_continuous(breaks = seq(500, 800, by = 50)) 
```
